\documentclass{resume}
\usepackage[left=0.6in,top=0.6in,right=0.6in,bottom=0.6in]{geometry}
\usepackage[svgnames]{xcolor}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  allcolors=DarkRed,
  pdfborderstyle={/S/U/W 1}
}

\usepackage{vwcol}
\usepackage{natbib}
\usepackage{cfr-lm}
\usepackage{graphicx}
\usepackage{enumitem}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TITLE SECTION
\begin{center}
    \name{Carolina Brañas}
    \contact
        {(+34)$\cdot$644$\cdot$004$\cdot$477}
        % {(+45)$\cdot$60$\cdot$90$\cdot$73$\cdot$33}
        {\href{mailto://carobrasor@gmail.com}{carobrasor@gmail.com}}
        {\href{https://carobs9.github.io/}{carobs9.github.io}}
        {\href{https://github.com/carobs9}{github.com/carobs9}}
        {\href{https://www.linkedin.com/in/carolinabranas/}{linkedin.com/in/carolinabranas}}
        {Copenhagen, Denmark}
        % {Madrid, Spain}
\end{center}

\begin{center}
    \textbf{Data Scientist} \\
    Passionate about machine learning, network analysis, natural language processing, and geospatial data science. \\
    Keen interest in data visualization and its role in communicating insights effectively.
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RESEARCH EXPERIENCE
\section{EXPERIENCE}
\begin{content}

    \begin{position}{University of Copenhagen}{May 2024 -- present}{Research Assistant in Data Science}{Prof.~Jeanet Bentzen}{}
    \item Contributed to the {\href{https://www.economics.ku.dk/research/externally-funded-research_new/shocking-religion/}{Shocking Religion}} project, analyzing economic effects of religious shocks.
    \item Constructed and deployed topic modeling solutions with SentenceTransformers and BERTopic; developed LLM-based pipelines using retrieval-augmented generation (RAG) for contextual document analysis.
    \item Conducted time series analysis and built visualizations to interpret long-term socioeconomic patterns.
    \item Presented findings through technical reports and presentations tailored to diverse audiences.
    \item Designed, dockerized, and deployed data solutions; leveraged UCloud to streamline large-scale data processing.
    \end{position}

    \begin{position}{Above Sports}{October 2023 -- May 2024}{Data Scientist}{}{}
    \item Built computer vision models to improve company’s logo detection tool.
    \item Collaborated on process automation and product performance enhancements.
    \end{position}

    \begin{position}{Crescendo Collective}{September 2021 -- May 2022}{Marketing Strategist}{}{}
    \item Conducted data analysis using Google Analytics and Ads, delivering actionable insights.
    \item Led market research and supported automation of internal analytics pipelines.
    \end{position}

\sectionlineskip
\end{content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EDUCATION 
\section{EDUCATION} 
\begin{content}
    {\bf University of Copenhagen} \hfill {\bf 2022 -- 2024} \\
    M.Sc. Social Data Science \\
    {\em Thesis:} {\href{https://carobs9.github.io/segregation-mobility/}{Mobility and income segregation in Madrid, Spain}} \\
    {\em Elective Courses:}
    \begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
        \item Advanced Machine Learning for Data Science (IT University of Copenhagen)
        \item Geospatial Data Science (IT University of Copenhagen)
        \item Advanced Network Science (IT University of Copenhagen)
        \item Natural Language Processing (Department of Computer Science, DIKU)
    \end{itemize}

    \medskip

    {\bf Cardinal Stritch University} \hfill {\bf 2018 -- 2022} \\
    B.Sc. Marketing, Minor in Computer Science \\
    {\em Dean's List (2018--2022)} \\
    {\em Best Graduating GPA in Marketing B.Sc. (2022)}

    {\bf Cardinal Stritch University} \hfill {\bf 2018 -- 2022} \\
    Minor in Computer Science \\
\sectionlineskip
\end{content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% AWARDS
\section{AWARDS} 
\begin{content}
    \prize{Dean's List}{2018 -- 2022}{}
    \prize{Best Graduating GPA of Marketing B.Sc.}{2022}{}
    \prize{Academic and Athletic Grant Through B.Sc.}{2018 -- 2022}{}
\sectionlineskip
\end{content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROJECTS
\section{PROJECTS \textbf{\em\&} EXTRACURRICULARS} 
\begin{content}

    \begin{position}{Mobility and Income Segregation in Madrid}{2023}{\href{https://github.com/carobs9/segregation-madrid}{github.com/carobs9/segregation-madrid}}{Master's Thesis project}{}
    \item Analyzed mobility and income segregation patterns using geospatial data, network analysis, and visual storytelling in Python.
    \end{position}

   %\begin{position}{LLM PDF Retrieval (RAG)}{2024}{\href{https://github.com/carobs9/llm-pdf-retrieval}{github.com/carobs9/llm-pdf-retrieval}}{}{Personal}
   %\item Built a retrieval-augmented generation (RAG) pipeline using LLMs to answer questions from PDFs. Focused on preprocessing, chunking, embedding, and vector search.
   %\end{position}

    \begin{position}{CycleGAN Monet}{2023}{\href{https://github.com/carobs9/CycleGAN_Monet}{github.com/carobs9/CycleGAN\_Monet}}{Academic project for Advanced Machine Learning course}{}
    \item Trained a CycleGAN model to convert real photos into Monet-style images. Implemented with PyTorch and conducted visual evaluation of stylization results.
    \end{position}
    
\sectionlineskip    
\end{content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TECHNICAL SKILLS
\section{SKILLS}
\begin{content}
    \begin{tabular}{ @{} >{\bf}l @{\hspace{6ex}} l }
        Programming Languages & Python (numpy, tensorflow, pytorch), SQL, Bash \\
        ML \& NLP & Transformers, Topic Modeling (umap, hdbscan, BERTopic), Scikit-learn, Hugging Face \\
        Geospatial Tools & Geopandas, Rasterio, QGIS \\
        Cloud/DevOps & UCloud, Docker, Git, Linux, VSCode \\
        Visualization & Seaborn, Matplotlib, PyPlot, Streamlit, Plotly, Bookeh, Tableau, Power BI, Geopandas \\
    \end{tabular}
\sectionlineskip
\end{content}

\end{document}
