\documentclass{resume}
% \showframe
\usepackage[left=0.6in,top=0.6in,right=0.6in,bottom=0.55in]{geometry}
\usepackage{vwcol}
\usepackage{cfr-lm}  % old-style numbers
\usepackage{natbib}
\setlength{\bibsep}{2.5pt}
\usepackage[svgnames]{xcolor}
\usepackage{hyperref}
\hypersetup{%
  colorlinks=true,
  allcolors=DarkRed,
  pdfborderstyle={/S/U/W 1}
}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TITLE
\begin{center}
    \name{Carolina Brañas}
    \contact
        {(+34)$\cdot$644$\cdot$004$\cdot$477}
        {\href{mailto://carobrasor@gmail.com}{carobrasor@gmail.com}}
        {\href{https://carobs9.github.io/}{carobs9.github.io}}
        {\href{https://github.com/carobs9}{carobs9}}
        {\href{https://www.linkedin.com/in/carolinabranas/}{carolinabranas}}
        {Copenhagen, Denmark}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EDUCATION 
\section{EDUCATION} 
\begin{content}
    {\bf UNIVERSITY OF COPENHAGEN} \hfill {\bf 2022 -- 2025} \\
    {M.Sc. Social Data Science} \\
    {\bf \em Thesis:} {\href{https://carobs9.github.io/segregation-mobility/}{Mobility and income segregation in Madrid, Spain.}}

    \medskip

    {\bf CARDINAL STRITCH UNIVERSITY} \hfill {\bf 2018 -- 2022} \\
    {B.Sc. Marketing, Minor in Computer Science} \\
    {\em Dean's List (2018--2022)} \\
    {\em Honours:} Best Graduating GPA of Marketing B.Sc. (2022)
\end{content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EXPERIENCE
\section{EXPERIENCE}
\begin{content}

    \begin{position}{UNIVERSITY OF COPENHAGEN}{May 2024 -- present}{Research Assistant in Data Science}{Prof.~Jeanet Bentzen}
        \item Working along a team of researchers for the project {\href{https://www.economics.ku.dk/research/externally-funded-research_new/shocking-religion/}{Shocking Religion}}, which examines the impact of religion on economic factors using shocks to religion as natural experiments.
        \item 
        \item Applied topic modeling using SentenceTransformers and BERTopic; developed retrieval-augmented generation (RAG) pipelines with LLMs for contextual document analysis.
        \item Conducted time series analysis on historical data and supported findings with statistical methods and visualizations.
        \item Communicated results through written reports and presentations to both technical and non-technical audiences.
    \end{position}

    \begin{position}{ABOVE SPORTS}{October 2023 -- May 2024}{Data Scientist}{}{}
        \item Collaborated on process automation and product performance improvements.
        \item Built computer vision models to enhance logo detection systems.
    \end{position}

    \begin{position}{CRESCENDO COLLECTIVE}{September 2021 -- May 2022}{Marketing Strategist}{}{}
        \item Conducted analysis using Google Analytics and Google Ads, delivering actionable reports.
        \item Researched market competition and automated internal processes with the data team.
    \end{position}

\end{content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% SKILLS 
\section{SKILLS} 
\begin{content}
    {\bf PROGRAMMING:} Python {\footnotesize (numpy, tensorflow, matplotlib, pytorch)}, SQL, Bash \\
    {\bf ML \& NLP:} Transformers, Topic Modeling {\footnotesize (umap, hdbscan, bertopic)}, Scikit-learn, Hugging Face \\
    {\bf GEOSPATIAL:} Geopandas, Rasterio, QGIS \\
    {\bf CLOUD / TOOLS:} UCloud, Git, Docker, Linux, VSCode
\end{content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% AWARDS
\section{AWARDS}
\begin{content}
    \prize{Dean's List}{2018--2022}{Achieved Dean’s List every semester of B.Sc. for a GPA above 3.5 with at least 12 credits.}

    \prize{Best Graduating GPA of Marketing B.Sc.}{2022}{Graduated with the top GPA (3.8/4.0) in Marketing.}

    \prize{Academic and Athletic Grant}{2018--2022}{Received a full scholarship for academic excellence and soccer performance over four years.}
\end{content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% OPTIONAL: PROJECTS
% Uncomment and fill in if you have real projects to showcase
% \section{PROJECTS}
% \begin{content}
%     \begin{project}{Project Title}{Date}
%         \item Describe the project and your contribution.
%     \end{project}
% \end{content}

\end{document}
